Automated Example Oriented REST API Documenation

### 2017-07-22 case_study/case_study.tex
fix the label/caption order
structurally complete, sans abstract / introduction / conclusion

\usetikzlibrary{backgrounds}
\pgfplotsset{compat=1.5}

@@

\subsection{Empirical Research on Web API evolution} % (fold)
\label{sub:empirical_research}
Several case study papers were published on Web API Evolution. Maleshkova et al. analyzed multiple Web APIs to identify the different approaches related to Web API descriptions, data formats, protocols, reusability, granularity, and authentication \cite{maleshkova}. They found that a lack of a standard format to document Web APIs and manual documentation led to API under-specification causing confusions about how to use the APIs for different use cases. They identified a need for automated approaches.

@@

\subsection{Techniques to evolve Web APIs} % (fold)
\label{sub:techniques}
Kaminski et al. presented a design technique called ``Chain of Adapters'' to implement evolving Web APIs \cite{kaminski2006design}. Using this approach, the source code of a Web API can evolve from a version to the next by introducing an adapter on the original version to implement any required change for new versions. This technique allows for multiple versions to be deployed concurrently since older versions are left unchanged.

@@

\subsection{Tool support for evolving Web APIs} % (fold)
\label{sub:tool_development}

@@

\begin{figure*}[!hbtp]
  \begin{subfigure}[b]{\textwidth}
    \def\dataSourceFileName{facebookx.dat}
    \begin{tikzpicture}[show background rectangle,tight background]
      \begin{axis}[
          ybar stacked,
          bar width=5pt,
          date coordinates in=x,
          xticklabel = \year-\month,
          xtick = {2013-01-09, 2013-04-01, 2013-07-01, 2013-10-01, 2014-01-01, 2014-04-01, 2014-08-01, 2014-07-02},
          xlabel style={font=\small},
          ylabel style={font=\small},
          ylabel={No. of Changes},
          xticklabel style= {rotate=90,anchor=near xticklabel,font=\tiny},
          enlarge x limits=false,
          height=0.20\textheight,
          width=\textwidth,
          legend style={legend pos=north west,font=\tiny, legend columns=4},
          legend to name=legend
        ]
        \input{case_study/change_frequency}
      \end{axis}
    \end{tikzpicture}
    \label{fig:facebook-chart}
    \caption{Facebook API Changes (11 Releases)}
  \end{subfigure}

  \begin{subfigure}[b]{\textwidth}
    \def\dataSourceFileName{stripe.dat}
    \begin{tikzpicture}[show background rectangle,tight background]
      \begin{axis}[
          date coordinates in=x,
          ybar stacked,
          bar width=5pt,
          xticklabel = \year-\month,
          xtick = {2011-09-15, 2012-01-01, 2013-01-01, 2014-01-01, 2014-10-01},
    %xlabel={Timeline},
          xlabel style={font=\small},
          ylabel style={font=\small},
          ylabel={No. of Changes},
          xticklabel style= {rotate=90,anchor=near xticklabel,font=\tiny},
          enlarge x limits=false,
          height=0.20\textheight,
          width=\textwidth,
          legend to name=legend
        ]
        \input{case_study/change_frequency}
      \end{axis}
    \end{tikzpicture}
    \label{fig:stripe-chart}
    \caption{Stripe API Changes (30 Releases)}
  \end{subfigure}

  \begin{subfigure}[b]{\textwidth}
    \def\dataSourceFileName{wordpress.dat}
    \begin{tikzpicture}[show background rectangle,tight background]
      \begin{axis}[
    %title=WordPress REST API Changes (8 Releases),
          date coordinates in=x,
          ybar stacked,
          bar width=5pt,
          xticklabel = \year-\month,
          xtick = {2013-08-07, 2013-11-01, 2014-03-01, 2014-06-26},
    %xlabel={Timeline},
          xlabel style={font=\small},
          ylabel style={font=\small},
          ylabel={No. of Changes},
          xticklabel style= {rotate=90,anchor=near xticklabel,font=\tiny},
          enlarge x limits=false,
          height=0.20\textheight,
          width=\textwidth,
          legend to name=legend
        ]
        \input{case_study/change_frequency}
      \end{axis}
    \end{tikzpicture}
    \label{fig:wordpress-chart}
    \caption{WordPress REST API Changes (8 Releases)}
  \end{subfigure}
  \begin{subfigure}[b]{\textwidth}
    \def\dataSourceFileName{github.dat}
    \begin{tikzpicture}[show background rectangle,tight background]
      \begin{axis}[
    %title=GitHub API Changes (59 Releases),
          date coordinates in=x,
          ybar stacked,
          bar width=5pt,
          xticklabel = \year-\month,
          xtick = {2012-09-05, 2012-12-01, 2013-03-01, 2013-06-01, 2013-09-01, 2013-12-01, 2014-03-01, 2014-10-06},
    %xlabel={Timeline},
          xlabel style={font=\small},
          ylabel style={font=\small},
          ylabel={No. of Changes},
          xticklabel style= {rotate=90,anchor=near xticklabel,font=\tiny},
          enlarge x limits=false,
          height=0.20\textheight,
          width=\textwidth,
          legend to name=legend
        ]
        \input{case_study/change_frequency}
      \end{axis}
    \end{tikzpicture}
    \label{fig:github-chart}
    \caption{GitHub API Changes (59 Releases)}
  \end{subfigure}

@@

  \begin{subfigure}[b]{\textwidth}
    \def\dataSourceFileName{gmap.dat}
    \begin{tikzpicture}[show background rectangle,tight background]
      \begin{axis}[
    %title=Google Maps Web API (102 Releases),
          date coordinates in=x,
          ybar stacked,
          bar width=5pt,
          xticklabel = \year-\month,
          xtick = {2011-01-06, 2011-07-01, 2012-01-01, 2012-07-01, 2013-01-01, 2013-07-01, 2014-01-01, 2014-07-01, 2014-09-18},
    %xlabel={Timeline},
          xlabel style={font=\small},
          ylabel style={font=\small},
          ylabel={No. of Changes},
          xticklabel style= {rotate=90,anchor=near xticklabel,font=\tiny},
          enlarge x limits=false,
          height=0.20\textheight,
          width=\textwidth,
          legend to name=legend
        ]
        \input{case_study/change_frequency}
      \end{axis}
    \end{tikzpicture}
    \label{fig:gmaps-chart}
    \caption{Google Maps Web API (102 Releases)}
  \end{subfigure}

  \begin{subfigure}[b]{\textwidth}
    \def\dataSourceName{Salesforce Force.com and Chatter REST}
    \def\dataSourceFileName{salesforce.dat}
    \begin{tikzpicture}[show background rectangle,tight background]
      \begin{axis}[
    %title=Salesforce REST API (4 Releases),
          date coordinates in=x,
          ybar stacked,
          bar width=5pt,
          xticklabel = \year-\month,
          xtick = {2013-10-04, 2014-01-01, 2014-04-01, 2014-07-01, 2014-10-18},
    %label={Timeline},
          xlabel style={font=\small},
          ylabel style={font=\small},
          ylabel={No. of Changes},
          xticklabel style= {rotate=90,anchor=near xticklabel,font=\tiny},
          enlarge x limits=false,
          height=0.20\textheight,
          width=\textwidth,
          legend to name=legend
        ]
        \input{case_study/change_frequency}
      \end{axis}
    \end{tikzpicture}
    \label{fig:salesforce-chart}
    \caption{Salesforce REST API (4 Releases)}
  \end{subfigure}

>>>>

\usetikzlibrary{backgrounds}
    \label{fig:screenshot_response}
\pgfplotsset{compat=1.5}

@@

\subsection{Empirical Research on Web API Evolution} % (fold)
\label{sub:empirical_research}
Several case study papers were published on Web API Evolution. Maleshkova et al. analyzed multiple Web APIs to identify the different approaches related to Web API descriptions, data formats, protocols, reusability, granularity, and authentication \cite{maleshkova}. They found that a lack of a standard format to document Web APIs and manual documentation led to API under-specification causing confusions about how to use the APIs for different use cases. They identified a need for automated approaches.

@@

\subsection{Techniques to Evolve Web APIs} % (fold)
\label{sub:techniques}
Kaminski et al. presented a design technique called ``Chain of Adapters'' to implement evolving Web APIs \cite{kaminski2006design}. Using this approach, the source code of a Web API can evolve from a version to the next by introducing an adapter on the original version to implement any required change for new versions. This technique allows for multiple versions to be deployed concurrently since older versions are left unchanged.

@@

\subsection{Tool Support for Evolving Web APIs} % (fold)
\label{sub:tool_development}

@@

\begin{figure*}[!hbtp]
  \begin{subfigure}[b]{\textwidth}
    \def\dataSourceFileName{facebookx.dat}
    \begin{tikzpicture}[show background rectangle,tight background]
      \begin{axis}[
          ybar stacked,
          bar width=5pt,
          date coordinates in=x,
          xticklabel = \year-\month,
          xtick = {2013-01-09, 2013-04-01, 2013-07-01, 2013-10-01, 2014-01-01, 2014-04-01, 2014-08-01, 2014-07-02},
          xlabel style={font=\small},
          ylabel style={font=\small},
          ylabel={No. of Changes},
          xticklabel style= {rotate=90,anchor=near xticklabel,font=\tiny},
          enlarge x limits=false,
          height=0.20\textheight,
          width=\textwidth,
          legend style={legend pos=north west,font=\tiny, legend columns=4},
          legend to name=legend
        ]
        \input{case_study/change_frequency}
      \end{axis}
    \end{tikzpicture}
    \caption{Facebook API Changes (11 Releases)}
    \label{fig:facebook-chart}
  \end{subfigure}

  \begin{subfigure}[b]{\textwidth}
    \def\dataSourceFileName{stripe.dat}
    \begin{tikzpicture}[show background rectangle,tight background]
      \begin{axis}[
          date coordinates in=x,
          ybar stacked,
          bar width=5pt,
          xticklabel = \year-\month,
          xtick = {2011-09-15, 2012-01-01, 2013-01-01, 2014-01-01, 2014-10-01},
    %xlabel={Timeline},
          xlabel style={font=\small},
          ylabel style={font=\small},
          ylabel={No. of Changes},
          xticklabel style= {rotate=90,anchor=near xticklabel,font=\tiny},
          enlarge x limits=false,
          height=0.20\textheight,
          width=\textwidth,
          legend to name=legend
        ]
        \input{case_study/change_frequency}
      \end{axis}
    \end{tikzpicture}
    \caption{Stripe API Changes (30 Releases)}
    \label{fig:stripe-chart}
  \end{subfigure}

  \begin{subfigure}[b]{\textwidth}
    \def\dataSourceFileName{wordpress.dat}
    \begin{tikzpicture}[show background rectangle,tight background]
      \begin{axis}[
    %title=WordPress REST API Changes (8 Releases),
          date coordinates in=x,
          ybar stacked,
          bar width=5pt,
          xticklabel = \year-\month,
          xtick = {2013-08-07, 2013-11-01, 2014-03-01, 2014-06-26},
    %xlabel={Timeline},
          xlabel style={font=\small},
          ylabel style={font=\small},
          ylabel={No. of Changes},
          xticklabel style= {rotate=90,anchor=near xticklabel,font=\tiny},
          enlarge x limits=false,
          height=0.20\textheight,
          width=\textwidth,
          legend to name=legend
        ]
        \input{case_study/change_frequency}
      \end{axis}
    \end{tikzpicture}
    \caption{WordPress REST API Changes (8 Releases)}
    \label{fig:wordpress-chart}
  \end{subfigure}
  \begin{subfigure}[b]{\textwidth}
    \def\dataSourceFileName{github.dat}
    \begin{tikzpicture}[show background rectangle,tight background]
      \begin{axis}[
    %title=GitHub API Changes (59 Releases),
          date coordinates in=x,
          ybar stacked,
          bar width=5pt,
          xticklabel = \year-\month,
          xtick = {2012-09-05, 2012-12-01, 2013-03-01, 2013-06-01, 2013-09-01, 2013-12-01, 2014-03-01, 2014-10-06},
    %xlabel={Timeline},
          xlabel style={font=\small},
          ylabel style={font=\small},
          ylabel={No. of Changes},
          xticklabel style= {rotate=90,anchor=near xticklabel,font=\tiny},
          enlarge x limits=false,
          height=0.20\textheight,
          width=\textwidth,
          legend to name=legend
        ]
        \input{case_study/change_frequency}
      \end{axis}
    \end{tikzpicture}
    \caption{GitHub API Changes (59 Releases)}
    \label{fig:github-chart}
  \end{subfigure}

@@

  \begin{subfigure}[b]{\textwidth}
    \def\dataSourceFileName{gmap.dat}
    \begin{tikzpicture}[show background rectangle,tight background]
      \begin{axis}[
    %title=Google Maps Web API (102 Releases),
          date coordinates in=x,
          ybar stacked,
          bar width=5pt,
          xticklabel = \year-\month,
          xtick = {2011-01-06, 2011-07-01, 2012-01-01, 2012-07-01, 2013-01-01, 2013-07-01, 2014-01-01, 2014-07-01, 2014-09-18},
    %xlabel={Timeline},
          xlabel style={font=\small},
          ylabel style={font=\small},
          ylabel={No. of Changes},
          xticklabel style= {rotate=90,anchor=near xticklabel,font=\tiny},
          enlarge x limits=false,
          height=0.20\textheight,
          width=\textwidth,
          legend to name=legend
        ]
        \input{case_study/change_frequency}
      \end{axis}
    \end{tikzpicture}
    \caption{Google Maps Web API (102 Releases)}
    \label{fig:gmaps-chart}
  \end{subfigure}

  \begin{subfigure}[b]{\textwidth}
    \def\dataSourceName{Salesforce Force.com and Chatter REST}
    \def\dataSourceFileName{salesforce.dat}
    \begin{tikzpicture}[show background rectangle,tight background]
      \begin{axis}[
    %title=Salesforce REST API (4 Releases),
          date coordinates in=x,
          ybar stacked,
          bar width=5pt,
          xticklabel = \year-\month,
          xtick = {2013-10-04, 2014-01-01, 2014-04-01, 2014-07-01, 2014-10-18},
    %label={Timeline},
          xlabel style={font=\small},
          ylabel style={font=\small},
          ylabel={No. of Changes},
          xticklabel style= {rotate=90,anchor=near xticklabel,font=\tiny},
          enlarge x limits=false,
          height=0.20\textheight,
          width=\textwidth,
          legend to name=legend
        ]
        \input{case_study/change_frequency}
      \end{axis}
    \end{tikzpicture}
    \caption{Salesforce REST API (4 Releases)}
    \label{fig:salesforce-chart}
  \end{subfigure}

### 2017-07-22 demo_paper/demo_paper.tex
structurally complete, sans abstract / introduction / conclusion

\begin{table}[!tbh]
  \caption{Examples of auto detected versions}
  \begin{tabular}{|p{0.2\linewidth}|p{0.5\linewidth}|p{0.2\linewidth}|}
    \hline
    \textbf{Type} & \textbf{Example Value} & \textbf{Detected version}\\
    \hline
    ``accept'' header & application/vnd.ex.ca.v3+json & v3\\
    \hline
    ``accept'' header & application/vnd.ex.ca.v3.1+json & v3.1\\
    \hline
    URL & \url{/v2/x} & v2\\
    \hline
    URL & \url{/v2.1/x} & v2.1\\
    \hline
    URL & \url{/v2.1-pre/users} & v2.1-pre\\
    \hline
  \end{tabular}
  \label{table:versions}
\end{table}

@@

\begin{figure*}[!tbh]
  \begin{mdframed}
    \centering
    \begin{subfigure}[t]{0.4\textwidth}
      \includegraphics[width=\linewidth]{summary.png}
      \caption{API documentation summary section}
      \label{fig:summary}
    \end{subfigure}
    \begin{subfigure}[t]{0.5\textwidth}
      \includegraphics[width=\linewidth]{examples.png}
      \caption{API documentation examples section}
      \label{fig:examples}
    \end{subfigure}
    \caption{SpyREST Screen shots showing auto generated API documentation}
    \label{fig:spyrest_screenshots}
  \end{mdframed}
\end{figure*}

@@

\subsection{Maintaining API Documentation for evolving APIs} % (fold)
Maintenance of RESTful API documentation is another use case of interest since the documentation for RESTful APIs need to evolve with the APIs to reflect the updated information. The 8 steps mentioned previously need to be repeated every time any of the API objects changes when a manual process is followed. Since APIs continue to evolve throughout their lifetime, manually maintaining their documentation incurs further costs or documentation can quickly become outdated.

>>>>

\begin{table}[!tbh]
  \caption{Examples of Auto Detected Versions}
  \begin{tabular}{|p{0.2\linewidth}|p{0.5\linewidth}|p{0.2\linewidth}|}
    \hline
    \textbf{Type} & \textbf{Example Value} & \textbf{Detected version}\\
    \hline
    ``accept'' header & application/vnd.ex.ca.v3+json & v3\\
    \hline
    ``accept'' header & application/vnd.ex.ca.v3.1+json & v3.1\\
    \hline
    URL & \url{/v2/x} & v2\\
    \hline
    URL & \url{/v2.1/x} & v2.1\\
    \hline
    URL & \url{/v2.1-pre/users} & v2.1-pre\\
    \hline
  \end{tabular}
  \label{table:versions}
\end{table}

@@

\begin{figure*}[!tbh]
  \begin{mdframed}
    \centering
    \begin{subfigure}[t]{0.4\textwidth}
      \includegraphics[width=\linewidth]{summary.png}
      \caption{API documentation summary section}
      \label{fig:summary}
    \end{subfigure}
    \begin{subfigure}[t]{0.5\textwidth}
      \includegraphics[width=\linewidth]{examples.png}
      \caption{API documentation examples section}
      \label{fig:examples}
    \end{subfigure}
    \caption{SpyREST Screenshots Showing Auto Generated API Documentation}
    \label{fig:spyrest_screenshots}
  \end{mdframed}
\end{figure*}

@@

\subsection{Maintaining API Documentation for Evolving APIs} % (fold)
Maintenance of RESTful API documentation is another use case of interest since the documentation for RESTful APIs need to evolve with the APIs to reflect the updated information. The 8 steps mentioned previously need to be repeated every time any of the API objects changes when a manual process is followed. Since APIs continue to evolve throughout their lifetime, manually maintaining their documentation incurs further costs or documentation can quickly become outdated.

### 2017-07-22 root.tex
remove unwanted files
controlled study paper is wholly included
boxes look good
adds the case study paper
adds the cisco study paper
demo paper is added
adds all 5 papers, reasonable ok formatted
structurally complete, sans abstract / introduction / conclusion

%% Modified documentstyle to documentclass -- compatibility with LaTex2e
%% N. Mancell (98/03/01).

%%  ucalgthes_root.tex        (NM 98/03/01)
%   Modified   92-09-18      Add references to dissertation        D. Teale
%                            Add approval page to toc
%                            Add ref to Title Degree on approval page
%   Modified  2006-09-12     Added geometry package to set up UofC thesis margins
%                            Removed includeprompt option N. Mancell
%
% Modified  2012-04-15  T.Zhang
% 1, the ‘fancy’ package is cancelled. The pagestyle is changed from ‘myheadings’ and ‘headings’ to ‘plain’ to move the page number (footer) from top right to bottom centre.
% 2, The parameter  of using ‘geometry’ package is changed from four different values (top=1in, bottom=1.22in, left=1.40in, right=0.850in) to one single value: 1in (top=1in, bottom= 1in, left= 1in, right= 1in)
% 3, ‘List of Figures’ is modified to ‘List of Figures and Illustrations’
% 4, A new page ‘List of Symbols, Abbreviations and Nomenclature’ is created. Its page number is following ‘List of Figures and Illustrations’ with Roman numerals. A separate file ‘symbols.tex’ is created for students to put content into the list.

\documentclass[12pt]{ucalgthes1}
\usepackage[letterpaper,top=1in, bottom= 1in, left= 1in, right= 1in]{geometry}
%\usepackage{fancyhdr}
%\fancyhead{}
%\fancyfoot{}
%\renewcommand{\headrulewidth}{0pt}
%\fancyhead[RO,LE]{\thepage}
%Define other usepackages here
\usepackage{hyperref}
\usepackage{mathptmx}
\title{Title of Thesis (title case, double spaced, no more than 240 characters. No bold font or symbols, except Greek) \\ \bigskip
Thesis Title Second Line }
%
%            Insert the correct information between the {}
%
\author{Student's Full Name}
\thesisyear{year}
\thesis{thesis}    % the word dissertation can be inserted between {}
\newcommand{\thesistitle}{Title of Thesis}
\monthname{month name}
\dept{GRADUATE PROGRAM IN "NAME OF PROGRAM"}
\degree{"FULL NAME OF DEGREE e.g.: DOCTOR OF PHILOSOPHY"}
%
%                    End of supplied information
%
\begin{document}
\makethesistitle
\pagenumbering{roman}     % resets page counter to one
\setcounter{page}{2}
%\chapter*{UNIVERSITY OF CALGARY \\ FACULTY OF GRADUATE STUDIES}
%\thispagestyle{empty}
%The undersigned certify that they have read, and recommend
%to the Faculty of Graduate Studies for acceptance, a \Thesis\ entitled
%``\thesistitle'' submitted by \Author\
%in partial fulfillment of the requirements for the degree of
%\Degree.\\

%
%                 Substitute  List of Examiners
%
%\begin{signing}{Department of Academic Computing}
%\signline
%Chairman, Dr.~John D.~Doe \\
%Department of Academic Computing \\
%Services  \\
%\signline
%Chairman, Dr.~John D.~Doe \\
%Department of Academic Computing \\
%Services  \\
%\signline
%Chairman, Dr.~John D.~Doe \\
%Department of Academic Computing \\
%Services  \\
%\signline
%Chairman, Dr.~John D.~Doe \\
%Department of Academic Computing \\
%Services  \\
%\newsigncolumn         use this command to start a new column if necessary
%\newsigncolumn
%\signline
%Chairman, Dr.~John D.~Doe \\
%Department of Academic Computing \\
%Services  \\
%\signline
%Dr.~Jane Smith \\
%Department of Academic Computing  \\

%\signline
%Dr.~A.~B.~Brown \\
%Department of Academic Computing  \\
%\end{signing}
%
\newpage
\phantomsection
\altchapter{\bf{Abstract}}
Paragraph 1

Paragraph 2

Paragragh 3

This page is required for all graduate theses.  An abstract is a short paragraph explaining the major points and conclusions of your thesis.  For master's theses, the abstract can be no more than 150 words long, while doctoral abstracts can be no longer than 350 words.

\newpage
\phantomsection
\altchapter{\bf{Acknowledgements}}
Paragraph 1

Paragraph 2

Paragraph 3

@@

\pagenumbering{arabic}
\include{chapter1}
%\include{chapter2}
%\include{chapter3}
%\include{chapter4}
%\include{chapter5}
\appendix
\include{appendix1}
\end{document}

>>>>

\documentclass[12pt]{ucalgthes1}
\usepackage[pdftex]{graphicx}
\usepackage[pdftex]{color}
\usepackage[letterpaper,top=1in, bottom= 1in, left= 1in, right= 1in]{geometry}
\usepackage{hyperref}
\usepackage{mathptmx}
\usepackage{listings}
\usepackage{url}
\usepackage[tableposition=top]{caption}
\usepackage{subcaption}
\usepackage{tikz,pgfplots,pgfplotstable}
\usepackage{mathtools}
\usepgfplotslibrary{dateplot}
\usepgfplotslibrary{statistics}
\usepackage{courier}
\usepackage[square,numbers,sectionbib]{natbib}
\usepackage[sectionbib]{chapterbib}
\usepackage[numbib]{tocbibind}
\newcommand{\newblock}{}
\usepackage{eurosym}
\usepackage{multirow}
\usepackage[T1]{fontenc}
\usepackage{textcomp}
\lstset{upquote=true}
\usepackage{float}
\floatstyle{boxed}
\usepackage{blindtext}
\let\labelindent\relax
\usepackage{upquote}
\usepackage{mdframed}
%\usepackage{balance}
\usepackage{enumitem}

\title{Automated Example Oriented REST API Documenation}
%
%            Insert the correct information between the {}
%
\author{S M Sohan}
\thesisyear{2017}
\thesis{thesis}    % the word dissertation can be inserted between {}
\newcommand{\thesistitle}{Automated Example Oriented REST API Documenation}
\monthname{September}
\dept{GRADUATE PROGRAM IN COMPUTER SCIENCE}
\degree{DOCTOR OF PHILOSOPHY}
%
%                    End of supplied information
%
\begin{document}
\makethesistitle
\pagenumbering{roman}     % resets page counter to one
\setcounter{page}{2}
\chapter*{UNIVERSITY OF CALGARY \\ FACULTY OF GRADUATE STUDIES}
\thispagestyle{empty}
The undersigned certify that they have read, and recommend
to the Faculty of Graduate Studies for acceptance, a \Thesis\ entitled
``\thesistitle'' submitted by \Author\
in partial fulfillment of the requirements for the degree of
\Degree.\\

%
%                 Substitute  List of Examiners
%
\begin{signing}{Department of Computer Science}
\signline
Dr. Frank Maurer \\
Supervisor\\
Department of Computer Science \\
University of Calgary \\
Canada\\
\signline
Dr. Mea Wang\\
Supervisory Committee Member\\
Department of Computer Science \\
University of Calgary \\
Canada\\
\signline
Dr. Craig Anslow\\
Supervisory Committee Member\\
School of Eng. and Computer Science \\
Victoria University of Wellington\\
New Zealand\\
\end{signing}
%
\newpage
\phantomsection
\altchapter{\bf{Abstract}}
\newpage
\phantomsection
\altchapter{\bf{Acknowledgements}}

@@

\pagenumbering{arabic}
\graphicspath{{controlled_study/}, {case_study/}, {cisco_study/}, {spy_rest/}, {demo_paper/}}
\pgfplotsset{table/search path={controlled_study,case_study}}
\renewcommand\bibname{References}
\chapter{Introduction}

\include{case_study/case_study}
\include{spy_rest/spy_rest}
\include{demo_paper/demo_paper}
\include{cisco_study/cisco_study}
\include{controlled_study/controlled_study}
\chapter{Conclusion}
\appendix
\end{document}

### 2017-07-22 spy_rest/spy_rest.tex
structurally complete, sans abstract / introduction / conclusion

\begin{figure*}[!tbh]
  \centering
  \begin{subfigure}[t]{0.4\textwidth}
    \includegraphics[width=\linewidth]{spyrest_header.png}
    \caption{API documentation summary section}
    \label{fig:summary}
  \end{subfigure}
  \begin{subfigure}[t]{0.5\textwidth}
    \includegraphics[width=\linewidth]{spyrest_examples.png}
    \caption{API documentation examples section}
    \label{fig:examples}
  \end{subfigure}
  \caption{SpyREST Screen shots showing auto generated API documentation}
  \label{fig:spyrest_screenshots}
\end{figure*}

@@

Fig \ref{fig:spyrest_screenshots} shows screen shots (shortened) from SpyREST auto generated documentation that is solely based on an example API call to URL \url{https://api.github.com/search/repositories?q=tetris+language:assembly&sort=stars&order=desc} with a custom header ``x-spy-rest-description'' to provide the short description for the example.

>>>>

\begin{figure*}[!tbh]
  \centering
  \begin{subfigure}[t]{0.4\textwidth}
    \includegraphics[width=\linewidth]{spyrest_header.png}
    \caption{API documentation summary section}
    \label{fig:summary}
  \end{subfigure}
  \begin{subfigure}[t]{0.5\textwidth}
    \includegraphics[width=\linewidth]{spyrest_examples.png}
    \caption{API documentation examples section}
    \label{fig:examples}
  \end{subfigure}
  \caption{SpyREST Screenshots Showing Auto Generated API Documentation}
  \label{fig:spyrest_screenshots}
\end{figure*}

@@

Fig \ref{fig:spyrest_screenshots} shows screenshots (shortened) from SpyREST auto generated documentation that is solely based on an example API call to URL \url{https://api.github.com/search/repositories?q=tetris+language:assembly&sort=stars&order=desc} with a custom header ``x-spy-rest-description'' to provide the short description for the example.
